An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-22 VLDB2026/main.tex
Update main.tex

	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.  CAPS shows a slight performance decline \underline{due to the increased query overhead caused by excessive} attribute-based grouping. In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction. 2) The complexity of StitchedVamana increases because data points may duplicate across multiple subgraphs. 3) The fusion distance of NHQ exhibits sensitivity to the number of attributes, which degrades its effectiveness. 4) UNG has poor performance because large number of entry points that need to be traversed. It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.

>>>>

	\textit{Effect of Multi-Attribute Building on Algorithm Performance (M vs. S).}
	As shown in Figure \ref{fig:exp_2_1}, Puck demonstrates nearly no performance degradation.  CAPS shows a slight performance decline \underline{due to the increased query overhead caused by excessive} attribute-based grouping. In contrast, the performance of StitchedVamana, FilteredVamana, NHQ, and UNG drops significantly, with the following reasons: 1) FilteredVamana increases the complexity introduced by retaining attribute during index construction. 2) The complexity of StitchedVamana increases \underline{because data points may duplicate across} \underline{multiple subgraphs}. 3) \underline{The fusion distance of NHQ exhibits sensitivity} \underline{to the number of attributes}, which degrades its effectiveness. 4) UNG has poor performance because large number of entry points that need to be traversed. It is difficult for a graph with multiple entries to have good connectivity, degenerating into a situation closer to inverted retrieval, and the effect may be greatly impaired.
